### 2020-04-21 draft_ABP.tex
Updates from Overleaf

(direct proof?)

@@

degenerations of $B_n$ ...

@@

>>>>

(better figure?)

One could use this construction of products to produce any finite product $\mathscr A_{i_1}\times \cdots \times \mathscr A_{i_k}$, and this construction is also valid for any generalized permutahderon. 
The direct proof of this argument for $\mathscr A_n$ is using the global $u$-equations of $\mathscr A_n$. ...

@@

The story of degenerations of $B_n$ is very similar. The first thing to do is to find degenerations whose big polytopes are simplices.

@@

The above  follows directly from the following relations amongst $u$ for each $I$ such that $0\notin I$ :
\bea
1-\prod_{I \subset J} u_{J} &=& \prod_{{J}\atop{J\cap \bar{I} \ne \emptyset}} u_{\bar{J}} \\
1-\prod_{J \subset I} u_{\bar{J}} &=& \prod_{I \subset J} u_{J} \prod_{J \subset \bar{I} } u_{\bar{J}}
\eea
\end{enumerate}
